The Hydrogen Epoch of Reionization Array (HERA)

### 2015-11-04 manuscript.tex
incremental but added specs table

\begin{table}
\label{tab:specs}
\caption{Overview of requirements and specifications}
\begin{tabular}{| l | l | c |}\hline
Parameter & Value & Comments \\ \hline
\end{tabular}
\end{table}

@@

\subsection{Spatial/Delay Response:  Diameter and Baselines}
The spatial response provides the defining characteristics for the experiment; related to the diameter, focal length, baseline, and configuration.  The principal constraint sets the delay response of the antenna element, characterized by the magnitude and frequency of the antenna ripple response.  This was initially addressed to first order in [MEMO] and in a much more detailed way in [UPCOMING PAPERS].  Expressed simply, the delay response of the antenna must be sufficiently attenuated such that the foreground signal levels at those delays is below the expected signal strength of the EOR signal.  This sets the optics and match needs.  As discussed in [REFS], this is addressed by direct measurement and modeling of the response to the system relative to and as a function of delay time from the initial wave reception.  The expected strength of the foregrounds is modeled through the system and plotted on the same set of axes.  These two regions should be disjoint to a significance of 60 dB.

@@

Interpreting these delay lines in Fig \ref{fig:costfig} is somewhat confusing, but note that the vertical color scale represents a fairly steep cost function preferring delay time-scales of less than 60 ns (ignoring the horizontal color scale, to be discussed in Sec \ref{sec:cost}).  The preliminary study requirement is to ensure that reflections are down by about 60 dB by that time-scale.  As seen by the black dashed line labelled '1' for one round-trip between the feed and vertex, for the focal ratio and diameters of interest  this reflection is always less than 60 ns, so this does not constrain the design.  For two round-trips (black solid line labelled '2'), we see that for diameters greater than 14.1m, the delay is less than 60 ns, so diameters less than this are preferred.  For three round-trips, we see that we would need antennas with diameters smaller than 9.4m.  However, cost (sec. \ref{sec:cost) and practicality issues ({\em i.e.}physically moving within the filled array) make these small diameters undesirable, so this means that we need to ensure that our system has sufficiently damped reflections for 3 reflections.  This is discussed in detail in UPCOMING PAPERS.

The minimum baseline is set such that the baseline has negligible impact on the minimum $k_{bin}$ (shown in Fig. \ref{fig:kperf}) in the standard analysis.  Somewhat arbitrarily, a maximum shortest baseline with equal contribution to $k_{min}$ at the full bandwidth of 100 MHz is chosen, which corresponds to about 15m.  Additionally, this baseline has been well-studied by the PAPER array (ref).

The above requirements also drive the specification on the element diameter, as well as the desire to maximize sensitivity.  This means that the diameter should be something around 15m (that is, a fully filled aperture for the minimum baseline).

@@

\subsection{Cost}
\label{sec:cost}
\begin{figure}[t]
\centerline{
\includegraphics[width=7.5cm]{plots/costfigNew.png} 
}
\caption{\small Costing model for a fixed sensitivity system as a function of diameter (thick blue line and left axis) as well as the round-trip delay for 1,2 and 3 feed-vertex trips (dashed red lines and right axis).  The 60 ns spec is indicated by the horizontal dash line, and the two-trip intersection at about 14-meter is the vertical dashed line.  SEE TEXT...
\label{fig:costfig}}
\end{figure}

>>>>

\begin{table}
\label{tab:specs}
\caption{Overview of requirements and specifications}
\begin{tabular}{| l | l | l | p{5cm} |}\hline
{\bf Parameter} & {\bf Requirement} & {\bf Value} & {\bf Comments} \\ \hline
Frequency range & 100 - 200 MHz & & Phase 1 \\ \hline
Number of channels & $>$256 & 1024 & \\ \hline
Diameter    & $<$ 14.1 m &  14.0 m & Picked near requirement for sensitivity/cost \\ \hline
Shortest baseline & $<$ 15 m & 14.6 m & \\ \hline
\end{tabular}
\end{table}

@@

\subsection{Spatial/Delay Response:  Diameter and Minimum Baseline}
The spatial response provides the defining characteristics for the experiment; related to the diameter, focal length, baseline, and configuration.  The principal constraint sets the delay response of the antenna element, characterized by the magnitude and frequency of the antenna ripple response.  This was initially addressed to first order in [MEMO] and in a much more detailed way in [UPCOMING PAPERS].  Expressed simply, the delay response of the antenna must be sufficiently attenuated such that the foreground signal levels at those delays is below the expected signal strength of the EOR signal.  This sets the optics and match needs.  As discussed in [REFS], this is addressed by direct measurement and modeling of the response to the system relative to and as a function of delay time from the initial wave reception.  The expected strength of the foregrounds is modeled through the system and plotted on the same set of axes.  These two regions should be disjoint to a significance of 60 dB.

@@

Interpreting Fig \ref{fig:costfig} is somewhat confusing, but note that the vertical color scale represents a fairly steep cost function preferring delay time-scales of less than 60 ns (ignoring the horizontal color scale for now, to be discussed in Sec \ref{sec:cost}).  The preliminary study requirement is to ensure that reflections are down by about 60 dB by that time-scale.  As seen by the black dashed line labelled '1' for one round-trip between the feed and vertex, for the focal ratio and diameters of interest  this reflection is always less than 60 ns, so this does not constrain the design.  For two round-trips (black solid line labelled '2'), we see that for diameters greater than 14.1m, the delay is less than 60 ns, so diameters less than this are preferred.  For three round-trips, we see that we would need antennas with diameters smaller than 9.4m.  However, cost (sec. \ref{sec:cost} and practicality issues ({\em i.e.}physically moving within the filled array) make these small diameters undesirable, so this means that we need to ensure that our system has sufficiently damped reflections for 3 reflections.  This is discussed in detail in UPCOMING PAPERS.  We have therefore adopted a specification that the antenna must be less than 14.1 meters in diameter.

The minimum baseline is set such that the baseline has negligible impact on the minimum $k_{bin}$ (shown in Fig. \ref{fig:kperf}) in the standard analysis.  Somewhat arbitrarily, a maximum shortest baseline with equal contribution to $k_{min}$ at the full bandwidth of 100 MHz is chosen, which corresponds to about 15m.  Additionally, this baseline has been well-studied by the PAPER array (ref) and is consistent with the diameter specification derived above.

\begin{figure}[t]
\centerline{
\includegraphics[width=7.5cm]{plots/costfigNew.png} 
}
\caption{\small Costing model for a fixed sensitivity system as a function of diameter (thick blue line and left axis) as well as the round-trip delay for 1,2 and 3 feed-vertex trips (dashed red lines and right axis).  The 60 ns spec is indicated by the horizontal dash line, and the two-trip intersection at about 14-meter is the vertical dashed line.  SEE TEXT...
\label{fig:costfig}}
\end{figure}

@@

\subsection{Cost}
\label{sec:cost}
